\huge{DRAFT} \\ ~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-13 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
first draft whitout plan

\begin{document}
\long\def\/*#1*/{}
\date{}%{\today}
\title{\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project}
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c}
	Briand X.\footnote{Isterre, Cnrs, email xav.briand@gmail.com}  & Bzeznik B.\footnote{Ciment, Universit\'e Joseph Fourier} \\
\end{tabular}}

\maketitle
%\thispagestyle{empty}

\subsection*{Abstract}
{\em
blabla
\\
\\
\\
\\
\\
blabla
}
\subsection*{Keywords}
Data-Intensive, grid computing, distributed storage, Seismic Noise, Whisper, Cigri, Irods.

\begin{multicols}{2}
%\/*
\section{Plan}
\begin{enumerate}
	\item Introduction, abstract (3\S , 1 page) 
  	\item Background (7-10\S, 1-2 pages)
    \begin{enumerate}
  	  \item The Whisper project
  	  \item Size of observational data
  	  \item Size of computational data
  	  \item General Big data/ science of  universe
  	  \item Coupling scientific objectives / IT constraints
  	  \item Data grid paradigm
  	  \item Data grid in Grenoble
  	  %\item Whisper organisation
  	  \item Collaboration Whisper/IT infrastructure
  	\end{enumerate}
  	\item Software for data-intensive processing (6-12\S , 1-2 pages)
  	\begin{enumerate}
      \item General IT codes whisper
      \item Computer language and librairies
      \item Structure of codes
      \item Package for raw data
      \item Package for correlations
      \item First optimisation of correlation
      \item Second optimisation of correlation
      \item Codes for analysis of correlations
      \item Where we can run the codes
    \end{enumerate}
  \item IT infrastrcuture for grid computing (6-12\S , 1-2 pages)
    \begin{enumerate}
  	  \item Needs of coupling storage computation
  	  \item Presentation Ciment
  	  \item Coupling Irods/Cigri
  	  \item Resulting Data-Grid
      \item Presentation Irods
	  \item General Infra Irods (diagram)
	  \item Effective Nodes Irods (diagram)
  	  \item General Cigri
  	  \item Mechanism with OAR
  	  \item Mechanism resubmission/besteffort
  	  \item Description of a campaign
  	  \item Low Interaction Cigri/Irods
  	  \item Cigri V2 and V3 functionalities
  	\end{enumerate}
  \item Results and feedback (28-31\S, 6-7 pages))
      \begin{enumerate}
	    \item Whisper Use Case
        \item Infrastructure Ciment experiences
       \end{enumerate}
\end{enumerate}
%*/

\newpage
\section{Background 7-10\S, 1-2 pages}
~\\

@@

\newpage

\section{Software for data-intensive processing (6-12\S , 1-2 pages) } \label{Section_Software_for_data-intensive_processing}
~\\

@@

%\end{multicols}
\begin{center}%[h]
\centering
\captionof{figure}{\label{whisperCorrelationStep} Step of the correlations}
\includegraphics[width=6cm]{schemaCorrelationStep.png}
\end{center}
%\begin{multicols}{2}

@@

\end{multicols}
\begin{figure}[h]
\centering
\caption{\label{whisperGeneralWorflow} Main sequences of processings of the Whisper Codes}
\includegraphics[width=16cm]{briandPosterAGU2013GimpProcessing.png}
\end{figure}

\newpage
\begin{multicols}{2}

\section{IT infrastructure for grid computing (6-12\S , 1-2 pages) }
~\\

@@

\newpage

@@

\newpage

\section{Results and feedback (28-31\S, 6-7 pages)}

\subsection{Whisper Use Case}

	\begin{enumerate}
	  \item Scientific whisper results: theses, articles, prices
  	  \item Organisation with a DataSet: Evaluation local/Ciment, capacities adaptation students
  	  \item Comparison data management, examples Japan processing/USArray 
  	  \item Evolution specification, genericty of the codes, degree of automatization
  	  \item First step: Conversion data format, distributions of datas on ressources: decrease the concurrency
  	  \item Back to the first package signal processing for Japan
  	  \item Identification seismogram: Dates, stations  / Modelization distribution: sublist Dates, Stations
  	  \item Adding python modules for data retrieve + Calls.
  	  \item Focus on encapsulation queries
      \item The file parameters
      \item the file start.bash
      \item The jdl file
  	  \item Back to the package correlation: similar adds 
  	  \item Focus on the distribution problem (Space complexity/Transfer)
  	  \item Focus on file size: flat/dictionnary
  	  \item Mode besteffort: increase of datas transfert, it possibly adds also new steps of data storage.
  	  \item Some order of magnitude for the Japan Computation.
  	  \item On the Japanese results.
  	\end{enumerate}

>>>>

\begin{document}
\long\def\/*#1*/{}
\date{}%{\today}
\title{\huge{DRAFT} \\ ~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project}
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c}
	Briand Xavier\footnote{Cnrs, Isterre, Whisper, email xav.briand@gmail.com}  & Bzeznik Bruno\footnote{Ciment, Universit\'e Joseph Fourier, Technical header of Ciment} \\
\end{tabular}}
\maketitle
%\thispagestyle{empty}

\subsection*{Abstract}
{\em

Like many projects in science of the universe, the seismological project Whisper is faced with massive data processing.
This leads to specific IT software for the project as well as suitable IT infrastructure. We present here both aspects.

We provide a flexible way to design a sequence of processing. We also deal with data-management and computational optimization questions.

On IT infrastructure, we present the platform Ciment provided by the University of Grenoble. It offers a data-grid environement with the 
distributed storage iRODS and the grid manager CiGri.

This is the partnership between these two IT components that has enabled a data-intensive processing and, also,  permits to the Whisper project to bring new scientific results.

}
{\bf Keywords}:  Data-Intensive, grid computing, distributed storage, Seismic Noise, Whisper, Cigri, Irods.

\begin{multicols}{2}
\/*
\section{Plan}
\begin{enumerate}
	\item Introduction, abstract (3\S , 1 page) 
  	\item Background (7-10\S, 1-2 pages)
    \begin{enumerate}
  	  \item The Whisper project
  	  \item Size of observational data
  	  \item Size of computational data
  	  \item General Big data/ science of  universe
  	  \item Coupling scientific objectives / IT constraints
  	  \item Data grid paradigm
  	  \item Data grid in Grenoble
  	  %\item Whisper organisation
  	  \item Collaboration Whisper/IT infrastructure
  	\end{enumerate}
  	\item Software for data-intensive processing (6-12\S , 1-2 pages)
  	\begin{enumerate}
      \item General IT codes whisper
      \item Computer language and librairies
      \item Structure of codes
      \item Package for raw data
      \item Package for correlations
      \item First optimisation of correlation
      \item Second optimisation of correlation
      \item Codes for analysis of correlations
      \item Where we can run the codes
    \end{enumerate}
  \item IT infrastrcuture for grid computing (6-12\S , 1-2 pages)
    \begin{enumerate}
  	  \item Needs of coupling storage computation
  	  \item Presentation Ciment
  	  \item Coupling Irods/Cigri
  	  \item Resulting Data-Grid
      \item Presentation Irods
	  \item General Infra Irods (diagram)
	  \item Effective Nodes Irods (diagram)
  	  \item General Cigri
  	  \item Mechanism with OAR
  	  \item Mechanism resubmission/besteffort
  	  \item Description of a campaign
  	  \item Low Interaction Cigri/Irods
  	  \item Cigri V2 and V3 functionalities
  	\end{enumerate}
  \item Results and feedback (28-31\S, 6-7 pages))
      \begin{enumerate}
	    \item Whisper Use Case
        \item Infrastructure Ciment experiences
       \end{enumerate}
\end{enumerate}
*/

\newpage
\section{Background}% 7-10\S, 1-2 pages}

@@

%\newpage

\section{Software for data-intensive processing} \label{Section_Software_for_data-intensive_processing} %(6-12\S , 1-2 pages) }

@@

%\end{multicols}
\begin{center}[h]
\centering
\captionof{figure}{\label{whisperCorrelationStep} Step of the correlations}
\includegraphics[width=6cm]{schemaCorrelationStep.png}
\end{center}
%\begin{multicols}{2}

@@

\end{multicols}
\begin{figure}[h]
\centering
\caption{\label{whisperGeneralWorflow} Main sequences of processings of the Whisper Codes}
\includegraphics[width=14cm]{briandPosterAGU2013GimpProcessing.png}
\end{figure}

\begin{multicols}{2}

\section{IT infrastructure for grid computing}% (6-12\S , 1-2 pages) }

@@

@@

\section{Results and feedback} % (28-31\S, 6-7 pages)}

\subsection{Whisper Use Case}
\/*
	\begin{enumerate}
	  \item Scientific whisper results: theses, articles, prices
  	  \item Organisation with a DataSet: Evaluation local/Ciment, capacities adaptation students
  	  \item Comparison data management, examples Japan processing/USArray 
  	  \item Evolution specification, genericty of the codes, degree of automatization
  	  \item First step: Conversion data format, distributions of datas on ressources: decrease the concurrency
  	  \item Back to the first package signal processing for Japan
  	  \item Identification seismogram: Dates, stations  / Modelization distribution: sublist Dates, Stations
  	  \item Adding python modules for data retrieve + Calls.
  	  \item Focus on encapsulation queries
      \item The file parameters
      \item the file start.bash
      \item The jdl file
  	  \item Back to the package correlation: similar adds 
  	  \item Focus on the distribution problem (Space complexity/Transfer)
  	  \item Focus on file size: flat/dictionnary
  	  \item Mode besteffort: increase of datas transfert, it possibly adds also new steps of data storage.
  	  \item Some order of magnitude for the Japan Computation.
  	  \item On the Japanese results.
  	\end{enumerate}
*/
